Visualizations for article

### 2018-07-28 notebooks/101-visualizations-for-article.Rmd
Adjust NY1850 most borrowed

NY1850_for_plotting %>% 
  # select(section = borrower_section, n) %>% 
  mutate(n = ifelse(n < 2, NA, n)) %>% 
  # mutate(n = cut(n, c(seq(0, 40, 5), 85))) %>% View
  mutate(n = cut(n, c(seq(0, 80, 10), max_n))) %>% 
  mutate(.,
         column = col_vector(nrow(.), 50),
         row = row_vector(nrow(.), 50)) %>% 
  ggplot(aes(x = column, y = -row, fill = n)) +
  geom_tile(color = "lightgray") +
  scale_fill_brewer(palette = "YlOrBr", na.value = "white", 
                    labels = c("2-10", "11-20", "21-30", "31-40", "41-50",
                               "51-60", "61-70", "71-80", "80+", "")) +
  labs(x = NULL, y = NULL, fill = "Number of similar sections in subsequent codes") + 
  coord_equal() + 
  theme_minimal() + 
  theme(legend.position = "bottom",
      axis.ticks = element_blank(),
      axis.line = element_blank(), axis.text = element_blank(),
      panel.background = element_blank(), panel.grid = element_blank(),
      legend.key.size = unit(0.5, "cm"),
      plot.margin = unit(c(0, 0, 0, 0), "cm"),
      plot.title = element_text(hjust = 0.5)) +
  labs(title = "Most influential sections in NY1850")
```

>>>>

NY1850_for_plotting %>% 
  # select(section = borrower_section, n) %>% 
  mutate(n = ifelse(n < 2, NA, n)) %>% 
  # mutate(n = cut(n, c(seq(0, 40, 5), 85))) %>% View
  mutate(n = cut(n, c(seq(0, 80, 10), max_n))) %>% 
  mutate(.,
         column = col_vector(nrow(.), 50),
         row = row_vector(nrow(.), 50)) %>% 
  ggplot(aes(x = column, y = -row, fill = n)) +
  geom_tile(color = "lightgray") +
  scale_fill_brewer(palette = "YlOrBr", na.value = "white", 
                    labels = c("2-10", "11-20", "21-30", "31-40", "41-50",
                               "51-60", "61-70", "71-80", "80+", "")) +
  labs(x = NULL, y = NULL, fill = "Number of similar sections\nin subsequent codes") + 
  coord_equal() + 
  theme_minimal() + 
  theme(legend.position = "bottom",
      axis.ticks = element_blank(),
      axis.line = element_blank(), axis.text = element_blank(),
      panel.background = element_blank(), panel.grid = element_blank(),
      legend.key.size = unit(0.5, "cm"),
      plot.margin = unit(c(0.0, 0.0, 0.0, 0.0), "cm"),
      plot.title = element_text(hjust = 0.5)) +
  labs(title = "Most influential sections in NY1850")
ggsave("out/diss/NY1850-most-borrowed.png", width = 6.5, height = 7.5)
```
